---
title: "Developing Data Products - Assignment 2 (Week 2)"
author: "Sanjay Somraj"
date: "Created Date: 14 June, 2017"
output:
  html_document:
    fig_height: 8
    fig_width: 8
    keep_md: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### BSE (formerly known as Bombay Stock Exchange Ltd.)

Established in 1875, BSE (formerly known as Bombay Stock Exchange Ltd.), is Asia's first & the Fastest Stock Exchange in world with the speed of 6 micro seconds and one of India's leading exchange groups. Popularly known as BSE, the bourse was established as "The Native Share & Stock Brokers' Association" in 1875.  

Over the past 141 years, BSE has facilitated the growth of the Indian corporate sector by providing it an efficient capital-raising platform.    

Today BSE provides an efficient and transparent market for trading in equity, currencies, debt instruments, derivatives, mutual funds. It also has a platform for trading in equities of small-and-medium enterprises (SME).  

BSE is also the 1st listed stock exchange of India.

BSE provides a host of other services to capital market participants including risk management, clearing, settlement, market data services and education. It has a global reach with customers around the world and a nation-wide presence.

### Historical - Indices
This plot presents the **BSE sensitivity index (Sensex)** points for the period 01 Jan 2012 - 31 Dec 2016. The user can select a specific period on the plot line to get a more detailed view on the BSE index movement.

The hover text displays - Date and High value followed by Open and Close Values.

### Reference
The BSE sensitivity index data was taken from the BSE site.
Read: http://www.bseindia.com/indices/IndexArchiveData.aspx#

&nbsp;
&nbsp;

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(plotly)
library(lubridate)

sensexData <- read.csv("./data/sensex.csv", stringsAsFactors = FALSE)
valueDate <- parse_date_time(sensexData$Date, orders = "dmy")
valueDate <- as.Date(valueDate)

x <- list(
     zeroline = TRUE,
     showline = TRUE,     
     zerolinecolor = toRGB("black"),
     zerolinewidth = 10,
     ticklen = 10,
     tickwidth = 2,
     tickcolor = toRGB("red"),
     size = 14,     
     title = "Time - Jan, 2012 : Dec, 2016"
)

y <- list(
     zeroline = TRUE,
     showline = TRUE,     
     zerolinecolor = toRGB("black"),
     zerolinewidth = 10,
     ticklen = 10,
     tickwidth = 2,
     tickcolor = toRGB("red"),
     title = "Sensex (High)"
)

sensexData$hover <- with(sensexData, paste("<br>Open: ",Open,"<br>Close: ",Close))

plot_ly(sensexData, x = ~valueDate, y = ~High, text = ~hover, type = 'scatter', 
        mode = 'lines') %>% layout(xaxis = x, yaxis = y)
```
&nbsp;
&nbsp;
&nbsp;

**Thank you.**
